\LARGE \bf A Semi-Automated Software Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-04-03 paper.tex
added ranges in participants and duration histograms (in scripts)

\begin{figure}[!h]
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	title={Videos by participant},
	xlabel={Number of participants},
	ylabel={Frequency (\# of videos)},
    ymin=-5,
	ymax=175,
	xtick=data,
	xticklabels from table={\byactors}{X}
	]
	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
	\end{axis}
	\end{tikzpicture}
	\caption{Distribution of videos in pre-processed prototype dataset by number of participants}
	\label{fig:vids-by-participant}
\end{figure}

>>>>

\begin{figure}[!h]
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	title={Videos by participant},
	xlabel={Number of participants},
	ylabel={Frequency (\# of videos)},
    ymin=-5,
	ymax=175,
	xtick=data,
	xticklabels from table={\byactors}{X},
	xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
	]
	\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
	\end{axis}
	\end{tikzpicture}
	\caption{Distribution of videos in pre-processed prototype dataset by number of participants}
	\label{fig:vids-by-participant}
\end{figure}
